---
title: "Metadata"
author: "Wells"
date: "2025-02-12"
output: html_document
---

Class exercise to import your project data into R
--Create a folder called "project" in your code folder
--Save this file to the "project" folder
--Move your Nexis spreadsheet to the folder
--Create a project file: File | New Project | *** select Existing folder | "project"
--After project.Rproj launches, then launch this file, metadata.Rmd, and complete the tutorial

**By doing this, you avoid the ring of hell where R can't find your data**


#load tidyverse, janitor, rio
```{r}

library(tidyverse)
library(janitor)
library(rio)
library(dplyr)
library(lubridate)
```
#Import your data 
```{r}

trump_dei_news<- rio::import("trump_dei_news.XLSX")

#import my stuff correctly 

```
# Clean names
```{r}
trump_dei_news <- trump_dei_news |>
  clean_names()  
  
```




How many rows and columns does this dataset has? 

```{r}

print(paste0("This dataset has ", nrow(trump_dei_news), " rows and ", ncol(trump_dei_news), " columns."))

```

Create a table that displays a count of the top 20 newspaper_city entries. Filter out the NA values. 

```{r}
top_newspapers <- trump_dei_news |>
  filter(!is.na(publication_4, publication_16)) |> 
  count(publication_4)|> 
  top_n(20, n) |>
  arrange(desc( n)) |>
print(top_newspapers)

#have a question about the columns named, publication_4 and publication_16, seem like similar columns having the corresponding names to the pub 4's column so should I delete the publication_16 column.
```


-Create a table that counts all entries by year.

*The sample data I got is from the same year (2025), I plan to download more data before next class and I plan to talk about how I should split up the categories in which I want to explore the recent presidential moves. 

```{r}
count_by_day <- trump_dei_news |> 
 count(published_date) 
  arrange(desc)
  
```


-Create a simple column ggplot chart that shows the total entries by year
```{r}
count_by_day|> 
  ggplot(aes(x = published_date, y = n)) +
  ylab("Top Newspapers Count") +
  xlab("") +
  geom_line(color = "steelblue", size = 1) +
  labs(title = "Total Entries By Day",
       subtitle = "Source: Nexis Uni Data ",
       caption = "Graphic by Tiasia Saunders, 2/16/2025")
```

 Tips/Tricks: 
 
 c() = stands for concatenate (or combine). It is used to create vectors by combining multiple values into a single vector
-c() = cut columns, can have multiple columns 
count = can have multiple column names in it, to count multiple values in a column 
 glimpse = to get a breakdown of columns, data types, and column value 
 date = y/m/d = standard date format (ex: mutate(date =as.Date(date, format = "%Y %m %d)))
 is.na(x): Checks if elements in x are NA (returns TRUE for missing values and FALSE for others).
!is.na(x): Negates the is.na() result, meaning it keeps non-NA values (returns TRUE for non-missing values and FALSE for NAs).
 


Response for Assignment 1: 

Armed with your data analysis, write a 250 word memo at the end of the R markdown document that summarizes your findings. Use this opportunity to ask questions or note any major flaws in the data.


All in all, I believe that I wanted to split my analysis into four overarching branches of how newspaper media is covering Donald Trumps latest actions: 
  Media/ Idelogical Framing of Trump's policies 
  Trump's Rhetoric and Public Responses To It 
  Trump's Policy Decisions on DEI/ Civil Rights 
   - Media portrayal of Trump’s cuts to DEI programs and their impact
  - Differences in terminology and framing across news sources
  - Coverage of Trump’s pardoning of January 6th insurrectionists and its implications
  International Media Cover of Trump's Global Policies 
  -How foreign news outlets report on Trump’s withdrawal from the WHO
  -Reactions to U.S. trade tariffs and economic policies under Trump
  -Differences in U.S. vs. international framing of Trump’s global impact
  
As of now, I think I will narrow my focus to Trumps policy decisions on DEI programs, and how international media are covering Trumps global policies. I believe that this will help me get an understanding of how international analysts are discussing Trump and the implications of his withdrewing from the World Health Organization and the Paris Climate Agreement plan. International media may draw parallels between his domestic rollbacks on diversity initiatives and his disengagement from global cooperation, framing them as part of a larger effort to reshape the U.S.'s role in both social and diplomatic areas. 

For my analysis, my dataset is pretty clean although I would change a few columns name, to make them more comprehensibale for me when working with the data. For my graph, I am not shoked that there were a spike of outlets discussing Trump's impact on DEI prgorams during the end of January considering that is when it happened. I would want to delete the publication_16 colunn becasue it is bascially the same as the publication_4 column. I would change the publication_type_5 to publicaiton_type. Additionally, I would change the publication_4 column's name to publication_outlet for more clarity. Lastly, I have downloaded other sets of articles that I think will help me with my new focus for the project. Please let me know what you think. 